Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-12 tex/paper1/paper1.tex
edits to the paper

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{Distribution of Fourier power at some sample frequencies as a
function of AIA waveband and location.}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} show the distributions of the logarithm of
the Fourier power for a small number of frequencies, for all the
pixels in each region.  The distributions all follow a normal
distribution approximately.  This indicates that the power in each
each at each frequency is approximately log-normally distributed.
This observation guides the choice of how to average the \PS\ over
each of the selected region.  Since the Fourier power is log-normally
distributed, the arithmetic mean of the Fourier power is biased by the
very largest powers.  Since the logarithm of the Fourier power is
approximately Gaussian-distributed, the mean value is a better
representation of the range of values in the data.  Hence the mean of
the logarithm of the Fourier power is used to describe the mean
\Fps\ of each region (note that this is also equivalent to the
geometric mean of the Fourier power.)

@@

\section{Details of the model fitting procedure}\label{sec:app:ind}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.
The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
defined by the data (Section \ref{sec:obs}).

As noted in Section \ref{sec:anal}, the logarithm of the Fourier power
for all regions is approximated by a normal distribution $N(\mu,
\sigma)$.  The maximum likelihood estimate of the mean and variance of
normal distribution are given by
\begin{equation}
\hat{\mu} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}(X_{i}-\hat{\mu})^{2}
\label{eqn:sigmamean}
\end{equation}
where $N_{pixel}$ is the number of pixels in each region.  The
estimated error in the estimated mean is
\begin{equation}
\sqrt{\hat{\sigma_{d}^{2}}}/\sqrt{N}
\label{eqn:errorsigmamean}
\end{equation}
where $N$ is the number of measurements taken.  This formula assumes
that the measurements taken are all independent of each other.
However, this is not the case for the Fourier power in any given
frequency.  This is because neighbouring pixels are highly likely to
be physically connected to each other, and so time-series in
neighboring pixels are likely to be strongly correlated (assuming that
the background structure exists over at least two pixels).  Secondly,
the point spread function of AIA spreads emission in one pixel over
its neighbors.  Therefore, the measurements used to generate an error
to the Fourier power are not independent.

Therefore, the number of effectively independent pixels is less than
the actual number of pixels in any one region.  The number of
effective independent pixels is estimated in the following way.  The
cross correlation $c(\tau)$ function between two randomly chosen
next-nearest neighbor pixels is calculated.  The cross correlation
coefficient measures the linear dependence of two time series $X(t)$
and $Y(t \pm \tau)$ at different lags $\tau$.  This is used to define
a coefficient of independence between next nearest neighbor,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  The
effective number of independent pixels in region is given by
\begin{equation}
\label{eqn:nind}
N_{ind}= 1 + \rho(N_{pixel}-1).
\end{equation}
The number of independent measurements $N$ is set to $N_{ind}$ in
Equation \ref{eqn:errorsigmamean}.  This gives a lengthscale for the
uncertainty in the mean Fourier \PS.

@@

A three step fitting process is used to fit Models 1 and 2 to the
data.
\begin{enumerate}
\item Model 1 is fit to the data using the distribution widths
  $\sigma_{d}$.  Since this is much wider than the estimated error in
  the mean, it allows the fitting algorithm to converge to an
  approximate fit solution.
\item The estimated values to the model parameters are then used as
  initial guesses to the second fit of Model 1, assuming the much
  narrower estimated error $\sigma_{d}/\sqrt{N}{ind}$.  This generates
  a better estimate to the parameters of the model fit.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.
\item Model 2 is fit to the data using the distribution widths
  $\sigma_{d}$, seeded with the maximum likelihood parameter values
  from Step 2 and the estimated $G(\nu)$ model parameters from Step 3.
\item Model 2 is fit to the data using the maximum likelihood model
  parameter values at Step 4 and the adjusted widths
  $\sigma_{d}/\sqrt{N}{ind}$.
\end{enumerate}

>>>>

\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{Distribution of Fourier power at some sample frequencies as a
function of AIA waveband and location.}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} show the distributions of the logarithm of
the Fourier power for a small number of frequencies, for all the
pixels in each region.  These distributions are centrally peaked, and
show a slightly heavier tail towards lower Fourier powers (negative
skew), and are slightly broader when compared to a Gaussian
distribution.  Plots of all these distribution show that they are all
unimodal.  These observations guide the choice of how to average the
\PS\ over each of the selected region.  The nature of these
distributions suggest that the arithmetic mean of the Fourier power is
biased by the very largest powers.  Therefore, the mean value of the
logarithm of the Fourier power is a better description of the range of
values in the data (this is equivalent to the geometric mean of the
Fourier power).  The \FPs\ used below are calculated from the mean
value of the logarithm of the Fourier power.

@@

\section{Fitting models to the \PS}\label{sec:app:ind}
In order to perform the fit, the noise in the mean \FPs\ must be
estimated.  To do that, the power distributions of Section \ref{???}
are considered.  Each measurement of the Fourier power at a given
pixel is not independent of the Fourier power at another pixel.  This
is because neighbouring pixels are highly likely to be physically
connected to each other, and so time-series in neighboring pixels are
likely to be strongly correlated (assuming that the background
structure exists over at least two pixels).  Also, the point spread
function of AIA spreads emission in one pixel over on to its
neighbors.  Secondly, the distributions are only approximately normal.

Let the standard error in the mean of samples from a distribution be
given by $\sigma_{mean}$.  It is defined as the standard deviation of
the sampling distribution of the mean:
\begin{equation}
\sigma_{mean} = \sigma / N
\label{eqn:sigmamean}
\end{equation}
where $\sigma$ is the standard deviation of the original distribution
and $N$ is the sample size.  This formula assumes that the
measurements taken are all independent of each other, which is not the
case for the Fourier power spectra studied here.  Hence the value of
$N$ cannot be set to the number of pixels in a region.

Hence, the number of effectively independent pixels time-series must
be calculated.  First, a pair of randomly chosen next-nearest neighbor
pixels are selected from the region.  Next nearest neighbor pixels are
chosen as close physical proximity is most likely to express the
strongest interdependence.  Next, the cross correlation $c(\tau)$
function between two randomly chosen next-nearest neighbor pixels is
calculated.  The cross correlation coefficient measures the linear
dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
lags $\tau$.  This is used to define a coefficient of independence
between the neighbors,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  This
procedure is repeated 10,000 and the mean value $\hat{\rho}$ is
calculated. The effective number of independent pixels in region is
given by
\begin{equation}
\label{eqn:nind}
N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
\end{equation}
The number of independent measurements $N$ is set to $N_{eff}$ in
Equation \ref{eqn:sigmamean}.

Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.
The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
defined by the data (Section \ref{sec:obs}).

@@

A three step fitting process is used to fit Models 1 and 2 to the
data.
\begin{enumerate}
\item Model 1 is fit to the data using the distribution widths
  $\sigma$.  Since this is much wider than the standard error in
  the mean, it allows the fitting algorithm to converge to an
  approximate fit solution.
\item The estimated values to the model parameters are then used as
  initial guesses to the second fit of Model 1, assuming the much
  narrower estimated error $\sigma/\sqrt{N_{eff}}$.  This generates
  a better estimate to the parameters of the model fit.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.
\item Model 2 is fit to the data using the distribution widths
  $\sigma_{d}$, seeded with the maximum likelihood parameter values
  from Step 2 and the estimated $G(\nu)$ model parameters from Step 3.
\item Model 2 is fit to the data using the maximum likelihood model
  parameter values at Step 4 and the adjusted widths
  $\sigma_{d}/\sqrt{N}{ind}$.
\end{enumerate}
